---
title: "R and Restful APIs "
author: jim rothstein
date: 
#output:  
#    pdf_document:
#      latex_engine:  lualatex  
#output:  html_document
output:
    pdf_document:  
        latex_engine: lualatex
        toc:  true
        toc_depth: 4
        keep_tex:  true
        number_sections: true
    beamer_presentation:
        latex_engine: lualatex
        toc:  true
#        incremental:  true
        keep_tex:  true
        highlight:  espresso  
        slide_level:  1
        includes:
          in_header:  preamble.tex
fontsize:  10pt
---

<!-- 
PURPOSE:   Create a .pdf that is BEAMER
BEAMER is tex file (?) so latex can be incorporated.
CREATE:     rmarkdown::render("001_first.Rmd)
VIEW:       :!zathura 001_first.pdf

Patience:   slow
-->

```{r setup, include=F, eval=T}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)

```

```{r set_hooks, include=F, eval=T}
# foo1 will be a function
library(knitr)
knit_hooks$set(foo1 = function(before, options, envir) {
  if (before) {
    paste0( '\\footnotesize _I appear before a chunk!_\n\n', '\\rule{3cm}{.4pt}')
  } else {
    '\\normalsize  \n\n_I am after a chunk..._'
  }
})
```

<!--        Begin       -->

### Shift in thinking:

   Normal workflow:  acquire database/cleanup/analyis

   Consider a different way:  R to extract specific pieces of information from a
   resource.


###  Window to otherwise closed software. 

Most websites are closed software:  You can not poke around in the internals.
API is way to open a close software system in specific ways and to specific users.


### First,  quick Examples with command line tool:   cURL

```{r slide_restful, child=c("slide_restful_examples.Rmd")}
```

<!--    small centered horizontal line (for visually clarity) -->
<!--    !so said NOT to use \centerline -->

\centerline{\rule{3cm}{.4pt}}

###   More About RESTFUL APIs
```{r what_are, child=c("slide_what_are_REST_API.Rmd")}
```

\rule{3cm}{.4pt}


###   To use APIs, what do you really need to know?
```{r what_technologies, child=c("slide_goal.Rmd")}
```


```{r, curl_intro, child=c("slide_curl_intro_github.Rmd")}
```



###  Creating APIs. 
```{r, curl_intro, child=c("slide_openAPI.Rmd") }
```

```{r xxx}
knitr::knit_exit()
```


<!--   R   Finally!    Show work through vignette for httr2? -->

#   We know some of the plumbing:  HTTP, API documentation, CURL ... 

##   Finally, Do this in R, httr2: 

https://httr2.r-lib.org

show httpbin.org
show github.com
##  EXAMPLE:   Basic GET in R
```{r, httr2_intro, child=c("slide_httr2_intro.Rmd")}
```



<!--    But wait !    Security  -->

#   
-   But how to include security?
    




<!--    Add a user of your code:   3 players:   User, your code, the server -->
#  One issue not to overlook:  3rd party Security
```{r, httr2_intro, child=c("slide_security.Rmd")}
```

#   So far, the user has been you - the Developer.  What if you want others to
use app?     They are going to give their username/password to your app.
```{r, httr2_intro, child=c("slide_oauth_intro.Rmd")}
```

Reference and Further Reading (


<!--    Practical difficulties - each API different -->

##  EXAMPLE    Use Github uses token (PAT) in R.

##  New problem:  each API server is different!
(Quote:   httr2:: docs)

## EXAMPLES:   Many (follow httr2:: vignette) + Google, Youtube ...


```{r, openAPI, child=c("slide_openAPI.Rmd")}
```

```{r, r_pkgs, child=c("slide_R_pkgs.Rmd")}
```

https://github.com/jimrothstein/docs/blob/master/misc_files/001_R_stats_tech_reading.md



```{r render1, eval=F, include=F}
{
file <- "000_TALK_CURL.Rmd"
file  <- normalizePath(file)
file
}
rmarkdown::render(file)
```
