---
title: "R and Restful APIs "
author: jim rothstein
date: 
#output:  
#    pdf_document:
#      latex_engine:  lualatex  
#output:  html_document
output:
    beamer_presentation:
        latex_engine: lualatex
        toc:  true
#        incremental:  true
        keep_tex:  true
        highlight:  espresso  
        slide_level:  1
        includes:
          in_header:  preamble.tex
fontsize:  8pt
---

<!-- 
PURPOSE:   Create a .pdf that is BEAMER
BEAMER is tex file (?) so latex can be incorporated.
CREATE:     rmarkdown::render("001_first.Rmd)
VIEW:       :!zathura 001_first.pdf

Patience:   slow
-->

```{r setup, include=F, eval=T}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)

```

```{r set_hooks, include=F, eval=T}
# foo1 will be a function
library(knitr)
knit_hooks$set(foo1 = function(before, options, envir) {
  if (before) {
      
    '\\tiny _I appear before a chunk!_\n\n'
  } else {
    '\\normalsize  \n\n_I am after a chunk..._'
  }
})
```

<!--        Begin       -->

# API and Restful APIs

##  API is way to open a close software system in specific ways and to specific
users.

#  Restful Examples
```{r examples, child=c("slide_restful_examples.Rmd")}
```


<!--  Cursory, limited explanation of Restful APIs 
    links for reader.

    REWRITE
    
-->

#   RESTFUL APIs
```{r what_are, child=c("slide_what_are_REST_API.Rmd")}
```

---


## DEFINITION  
(from Wikipedia)https://en.wikipedia.org/wiki/Representational_state_transfer#Applied_to_web_services

>   Web service APIs that adhere to the REST architectural constraints are called RESTful APIs.[12] HTTP-based RESTful APIs are defined with the following aspects:[13]

  - a base URI, such as http://api.example.com/;
  - standard HTTP methods (e.g., GET, POST, PUT, and DELETE);
  - a media type that defines state transition data elements (e.g., Atom, microformats, application/vnd.collection+json,[13]: 91–99  etc.). The current representation tells the client how to compose requests for transitions to all the next available application states. This could be as simple as a URI or as complex as a Java applet.[14]

---

<!-- As practical matter, what do we need to know? --> 

#   Really need to know?

No R libraries (wrapper) for Github API


<!--    GOAL  write in R-->

# Goal:   Use R to programmatically retrieve data for analysis, securely.

```{r goal, child=c("slide_goal.Rmd"), foo1="whatever"}
```

---

<!-- So To GET to the GOAL .... Things to KNOW-->

#  What technologies are APIs built upon?
```{r what_technologies, child=c("slide_technologies.Rmd")}
```

---

#   HTTP Diagram
```{r, http, child=c("slide_http.Rmd")}
```

---

# API documenation
Endpoints:  
https://docs.github.com/en/rest/overview/endpoints-available-for-github-apps
https://developers.google.com/youtube/v3/docs/playlists/list
---

<!--  important of CURL  -->

CURL intro (using httpbin.org) 
do in browser, 
then in curl
compare: curl -is httpbin.org vs httpbin.org/get

browser:  show curl

```
curl -sv http://httpbin.org 
```
#  CURL intro (using Github)  (Live)

```{r, curl_intro, child=c("slide_curl_intro_github.Rmd"), include=F, eval=F}
```

---


<!--   R   Finally!    Show work through vignette for httr2? -->

#   We know some of the plumbing:  HTTP, API documentation, CURL ... 

##   Finally, Do this in R, httr2: 

https://httr2.r-lib.org

show httpbin.org
show github.com
##  EXAMPLE:   Basic GET in R
```{r, httr2_intro, child=c("slide_httr2_intro.Rmd")}
```

---
#   json

```{zsh, foo1="whatever"}
curl -s https://api.github.com/users/jimrothstein | head
```

#   json, -i includes headers
```{zsh}
curl -si https://api.github.com/users/jimrothstein | head
```

---

<!--    But wait !    Security  -->

#   
-   But how to include security?
    
#  GITHUB Personal Access Token (PAT)
```{r, httr2_intro, child=c("slide_PAT.Rmd")}
```
-   EXAMPLE:    Github token (Personal Access Token) (walk through)
-   Read the Documentation
-   SCOPE
-   Back to CURL
<!--    Github's PAT -->

#   Github PAT token
Why a token?

settings | developer settings (bottom left)

more info:
get token: https://docs.github.com/en/rest/guides/getting-started-with-the-rest-api

https://docs.github.com/en/rest
```{zsh, echo=T}
export token=$(Rscript -e "cat(Sys.getenv('GITHUB_PAT'))")
# echo $token

curl -si -u jimrothstein:$token https://api.github.com/users/jimrothstein |
head
```

# store the token ~/.Renviron
#   token, works
```{zsh, echo=T}
# Authorization?
export token=$(Rscript -e "cat(Sys.getenv('GITHUB_PAT'))")
echo $token
curl -Hs "Authorization: token $token" https://api.github.com/users/codertocat -I
```




<!--    So far, consumer of APIs.   How to produce APIs -->

#   There is another side to all this:  the Creater of APIs.
R has a tool `plumber`.   
Not for today.



<!--    Add a user of your code:   3 players:   User, your code, the server -->
#  One issue not to overlook:  3rd party Security
```{r, httr2_intro, child=c("slide_security.Rmd")}
```

#   So far, the user has been you - the Developer.  What if you want others to
use app?     They are going to give their username/password to your app.
```{r, httr2_intro, child=c("slide_oauth_intro.Rmd")}
```


<!--    Practical difficulties - each API different -->

##  EXAMPLE    Use Github uses token (PAT) in R.

##  New problem:  each API server is different!
(Quote:   httr2:: docs)

## EXAMPLES:   Many (follow httr2:: vignette) + Google, Youtube ...


```{r, openAPI, child=c("slide_openAPI.Rmd")}
```

```{r, r_pkgs, child=c("slide_R_pkgs.Rmd")}
```

```{r end2}
#knitr::knit_exit()
```


```{r render, eval=F, include=F}
{
file <- "002_API_R_talk.Rmd"
file  <- normalizePath(file)
file
}
rmarkdown::render(file, output_dir = "~/Downloads/print_and_delete")
```
