--- 
title: Template for .Rmd 
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"
output: 
  pdf_document: 
    latex_engine: lualatex
toc: TRUE 
toc_depth:  1 
fontsize: 10pt 
geometry: margin=0.5in,top=0.25in 
TAGS:  httr,
---

PURPOSE:    httr:: package, show all videos in one playlist

*  HEAD shows what is being sent (see the simple error?)
*  httr::HEAD("https://www.googleapis.com/youtube/v3/playlists",
 							query= query,
 							config = config) 

REF : 
https://www.r-bloggers.com/2019/01/how-to-authenticate-using-oauth2-through-r-2/
```{r setup, include=FALSE 		}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "      ##",
  error = TRUE,
  collapse = TRUE
)
load_all()
library(httr)
```

```{r endpoints1}
if (F) {
  # remove old .httr-oauth (till I know what I am doing)
  file.remove(".httr-oauth")
}

# be sure enabled
base::options("httr_oauth_cache" = TRUE)

# https://developers.google.com/accounts/docs/OAuth2InstalledApp
```

#### Google endpoints
```{r endpoints}
httr::oauth_endpoints("google")
# <oauth_endpoint>
#  authorize: https://accounts.google.com/o/oauth2/auth
#  access:    https://accounts.google.com/o/oauth2/token
#  validate:  https://www.googleapis.com/oauth2/v1/tokeninfo
#  revoke:    https://accounts.google.com/o/oauth2/revoke
```

## Create & Register myapp with Google
```{r register}
#  Security:  key & secret are in ~/.Renviron ( do not push to github )
#  NOTE:  google calls this key as "Client ID"
#   Rmk:   key is visible in myapp

myapp <- httr::oauth_app(
  "google",
  key <- Sys.getenv("OAUTH2_ID"),
  secret <- Sys.getenv("OAUTH2_SECRET")
)


# myapp
```

## SCOPES, auth.code
  - Create .httr-oauth (binary) in project root.

##  SCOPE 3 (BEST)
  - USE THIS auth.code for most work
  - Add scope for various youtube access.
  - youtube.force-ssl needed to retrieve user's playists, videos in each
```{r youtube_scopes}
#
{
  scope <- c("https://www.googleapis.com/auth/youtube.force-ssl")

  # c("https://www.googleapis.com/auth/userinfo.profile",
  # "https://www.googleapis.com/auth/userinfo.email",
  # "https://www.googleapis.com/auth/youtube",  # manage
  # "https://www.googleapis.com/auth/youtube.readonly",
  # "https://www.googleapis.com/auth/youtube.force-ssl"
  #  )
}
```  

## Get auth.code | token ....
```{r get_auth.code}
# NO .httr-oauth?  |  THEN pop, asks users,  AND warns not verified, not safe

# Rmk1:  option("httr_oauth_cache") was set to TRUE , token will then know to store
auth.code <- httr::oauth2.0_token(
  endpoint = httr::oauth_endpoints("google"),
  app = myapp,
  # cache = getOption("httr_oauth_cache"),
  cache = T,
  scope = scope
)

auth.code
```


# ============
##### Videos in one playlist
# ============


### return structure with all params
```{r prelim}
## if you need:
# playlists  <- readRDS(playlists, file=here("data","playlists.RDS"))

## documentary playlist
## list=PLbcglKxZP5POssPWRwjJff_vOY3o8eWdI
```

```
# REFERENCE
# curl \
#   'https://youtube.googleapis.com/youtube/v3/playlistItems?part=snippet%2CcontentDetails&playlistId=PLbcglKxZP5PNx1CGmLKT68vKELqrhj4hY&fields=pageInfo&key=[YOUR_API_KEY]' \
#   --header 'Authorization: Bearer [YOUR_ACCESS_TOKEN]' \
#   --header 'Accept: application/json' \
#   --compressed
```

```{r initiatize}
type <- "videos"

## to get all videos, for ONE playlist
global_params <- initialize()
global_params
```


#### No S3, construct one generic query.
```{r generic_query}
generic_q <- function() {
  ## query_defaults (starter values)
  if (!exists("query_defaults")) query_defaults <- get_typical_values()

  ## put it all togehter
  list(
    ## from global_params
    key = global_params$api$api_key,

    ## for videos:
    base_url = "https://www.googleapis.com/youtube/v3/playlistItems",
    part = "snippet",
    ## only change
    fields = "pageInfo.totalResults",

    # fields=paste(sep=",", "nextPageToken",
    #                  "items(id,snippet(title,description,publishedAt))"),


    ## from query_defaults (only what comments needs)
    maxResults = query_defaults$maxResults,
    channelId = query_defaults$channelId,
    playlistId = "PLbcglKxZP5PN3RCRdidmIxRrB8luufWIW", # gloria dehaven

    ## don't forget
    pageToken = NULL
  )
}


query_params <- generic_q()
query_params
```

#### Based on type, we now modify query_params list.
```{r modify_params}
# =============================
## assume type = "videos"
# =============================

query_params$fields <- paste(
  sep = ",", "nextPageToken",
  "items(id,snippet(title,description,publishedAt))"
)

query_params$playlistId <- "PLlXfTHzgMRUIqYrutsFXCOmiqKUgOgGJ5" # Pavel Grinfeld, Linear Alg 3

## documentary playlist
query_params$playlistId <- "PLbcglKxZP5POssPWRwjJff_vOY3o8eWdI"

query_params

## spares
## query_params$playlistId  <- "PLbcglKxZP5PMU2rNPBpYIzLTgzd5aOHw2"
# playlistId  <- "PLbcglKxZP5PN3RCRdidmIxRrB8luufWIW"  # gloria dehaven
# spare:
# query_params$playlistId =    "PLbcglKxZP5PN3RCRdidmIxRrB8luufWIW"  # gloria dehaven
# playlistId  <-  "PLlXfTHzgMRUIqYrutsFXCOmiqKUgOgGJ5"  # Pavel Grinfeld, Linear Alg 3
# videoId  <- "Mec9sw1cJk8"  # carter
# playlistId  <- "PLbcglKxZP5PMZ7afIT7E2o9NwQIzqTI5l"
## documentary playlist
## list=PLbcglKxZP5POssPWRwjJff_vOY3o8eWdI
```




#### Have everything, pack into bundle (3 elements)
```{r pack}
bundle <- list(
  url = query_params$base_url,
  config = global_params$config,
  query = query_params
)

bundle$url
bundle$config
bundle$query
```
### get_batch_videos
```{r next_batch}
get_batch <- function(url = NULL, query = NULL, config = NULL) {
  r <- httr::GET(
    url = url,
    query = query,
    config = config,
    httr::verbose()
  )


  ## process resonse, return table
  ## process(x = videos, r=r, videosdb = videosdb)
}
```

#### No S3, process batch
```{r process}
# ======================
##  assume type=videos
# ======================

process <- function(r = NULL, type = NULL, db = NULL) {
  json_content <- get_json(r)

  if (type == "videos") {
    db <- json_content$items$snippet
    nextPageToken <- json_content$nextPageToken
    list(
      nextPageToken = nextPageToken,
      db = db
    )
  }
}
```


## sample call
##    process(r = r, type = "videos", db = )

```

#### combine 1st batch + additional (if any)
```{r all_videos_ONE_playlist}
## run 1st time (may refresh stale token)

db <- NULL
r <- get_batch(url = bundle$url, query = bundle$query, config = bundle$config)
r <- process(r = r, type = "videos", db = db)
db <- r$db
nextPageToken <- r$nextPageToken

## Continue to get batches till null Token
while (!is.null(nextPageToken)) {
  bundle$query$pageToken <- nextPageToken
  r <- get_batch(url = bundle$url, query = bundle$query, config = bundle$config)
  r <- process(r = r, type = "videos", db = db)
  db <- rbind(db, r$db)
  nextPageToken <- r$nextPageToken
}

## finally
#  db


## videos  <- get_playlist_videos(playlistId)
str(db)
print(db$title)


#   View(db)
```


```{r}
saveRDS(db, file = here::here("data/videosdb.RDS"))
```

```{r}

```
cleanup videos
```{r cleanup, include=F, eval=F}
t <- videos %>%
  dplyr::select(title, position) %>%
  dplyr::arrange(title)
t
str(t)
```



```{r render, eval=FALSE, include=F	} 
file <- "/home/jim/code/youtube_api/httr2_pkg/000_httr_youtube_playlist_TALK.Rmd"

rmarkdown::render(file,
  output_dir = "~/Downloads/print_and_delete"
)
```
