--- 
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"
output: 
  html_document:
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document:   
    latex_engine: lualatex  
    toc: true
    toc_depth:  4   
    keep_tex:  true  
    keep_md:   true  
  header-includes:  
    -  \usepackage{helvet}  
    -  \renewcommand{\familydefault}{\sfdefault}  
    -  \usepackage{ulem}
fontsize: 10pt   
geometry: margin=0.4in,top=0.25in   
TAGS:  httr2,
---
PURPOSE:    HTTR2::   practice with OAUTH2 google People API
Reproduce what browser can do.


REF : 
Google:   project;  jrGooglePeopleapi
https://httr2.r-lib.org/articles/httr2.html
```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)
library(httr2)
load_all()
```

####    G- API key, obfuscate, other Useful, collect here

####    For Google People API
```{r usefu}
client_id="358088442289-amr4b5f5l1h9jicffu12d9t1vooiv10d.apps.googleusercontent.com"

# auth
endpoint = "https://accounts.google.com/o/oauth2/v2/auth"
scope="https://www.googleapis.com/auth/userinfo.profile"


## from httr:   useful?
  httr::oauth_endpoints("google")
# <oauth_endpoint>
#  authorize: https://accounts.google.com/o/oauth2/auth
#  access:    https://accounts.google.com/o/oauth2/token
#  validate:  https://www.googleapis.com/oauth2/v1/tokeninfo
#  revoke:    https://accounts.google.com/o/oauth2/revoke


secret  <-  "Well it is a secret"

# to hide it:
obfuscate(secret)
# obfuscated("3UwucEbpj75RVE33K_zutT4j7iPfsogxPuGLfZ-YhyukWNs")
```


#### Step #1, get auth code (via browser)
````{r}

```
Put into browser to (1) authorize (2) return AUTH CODE
Goal:  Do it R.

```

````

####    Create client to youtube
```{r client}

PEOPLE_CLIENT_ID  <- Sys.getenv("PEOPLE_CLIENT_ID")
PEOPLE_CLIENT_SECRET  <- Sys.getenv("PEOPLE_CLIENT_SECRET")

## paste this string into browser, get AUTH CODE
paste_into_browser <- paste0("https://accounts.google.com/o/oauth2/v2/auth?client_id=", PEOPLE_CLIENT_ID, 
       "&redirect_uri=urn:ietf:wg:oauth:2.0:oob&scope=https://www.googleapis.com/auth/userinfo.profile&response_type=code")



# then paste the reply,   here
auth.code ="4/1AX4XfWiQxltLCQV8QGTi2sZ5fnVMEgj6PMhWp46911_nVQMv4aSD7RFcZq4"
```
#### Exchange the auth.code for a token
```{r get_token}
## assemble a POST
data  <- paste0("code=", auth.code, "&client_secret=", PEOPLE_CLIENT_SECRET, 
                "&redirect_uri=urn:ietf:wg:oauth:2.0:oob",
                "&grant_type=authorization_code")
data


url  <- "https://accounts.google.com/o/oauth2/token" 

req  <- request(base_url = url ) %>% httr2::req_body_raw(body=data)
req |> req_dry_run()
req |> req_perform()


```

myapp = httr2::oauth_client(
        id =    client_id,
        token_url = endpoint, 
        name = "first_people_api"            
    )

myapp


```
```{r}

```{r token}
token  <-   oauth_flow_auth_code(client = myapp, 
                     auth_url = "https://accounts.google.com/o/oauth2/auth",
                     scope = scope
                     )
token
```


##  LEGACY
#### GET can have header, query, not body
#### get a req object, using httpbin, GET http://httpbin.org
```{r}
##  return what is sent
req <- request("https://httpbin.org/get")
req

## tack on query
req2 <- request("https://httpbin.org/get?q=joe")
req2

## now build, httr2 adds default headers
req %>% req_dry_run()


##  quote works
req |> req_headers(name =  "jim", location =  quote(eugene) )
```

### LEGACY
```{r endpoints}
if (F) {

# remove old .httr-oauth (till I know what I am doing)
  file.remove(".httr-oauth")

}

# be sure enabled
  base::options("httr_oauth_cache" = TRUE) 

# https://developers.google.com/accounts/docs/OAuth2InstalledApp
  httr::oauth_endpoints("google")
```

## Create & Register myapp with Google
```{r register}
#  Security:  key & secret are in ~/.Renviron ( do not push to github )
#  NOTE:  google calls this key as "Client ID"
#   Rmk:   key is visible in myapp

  myapp <- httr::oauth_app("google",
    key  <- Sys.getenv("OAUTH2_ID"),
    secret  <- Sys.getenv("OAUTH2_SECRET")
  )


  myapp
```

## SCOPES, auth.code
  - Create .httr-oauth (binary) in project root.

##  SCOPE 3 (BEST)
  - USE THIS auth.code for most work
  - Add scope for various youtube access.
  - youtube.force-ssl needed to retrieve user's playists, videos in each
```{r youtube_scopes}
#  
{
scope = 
  c("https://www.googleapis.com/auth/userinfo.profile",
  "https://www.googleapis.com/auth/userinfo.email",
  "https://www.googleapis.com/auth/youtube",  # manage
  "https://www.googleapis.com/auth/youtube.readonly",
  "https://www.googleapis.com/auth/youtube.force-ssl"
   )
}
 ```  
## Get auth.code | token ....
```{r get_auth.code}
# NO .httr-oauth?  |  THEN pop, asks users,  AND warns not verified, not safe

# Rmk1:  option("httr_oauth_cache") was set to TRUE , token will then know to store
  auth.code <- httr::oauth2.0_token(
              endpoint = httr::oauth_endpoints("google"),
              app = myapp,
              #cache = getOption("httr_oauth_cache"),
              cache = T,
              scope = scope
)

auth.code
```

#### Examine token in .httr-oauth
```{r check_token}
x  <- readRDS(".httr-oauth")
x
names(x)
length(x)
```



# ============
##### LEGACY
# ============

Simplest Scope

```{r .httr-oauth}

# sometimes this pops  up, too.
auth.code <- httr::oauth2.0_token(
              endpoint = httr::oauth_endpoints("google"),
              app = myapp,
              scope = "https://www.googleapis.com/auth/userinfo.profile")

```

## Is auth.code valid?
See 011_httr_check_valid_token.Rmd


#### now use GET, Works
#### TODO:  review httr commands here...
```{r use_api}
req <- httr::GET(
  "https://www.googleapis.com/oauth2/v1/userinfo",
  httr::config(token = auth.code) )

httr::stop_for_status(req)
str(httr::content(req))

### Compare to
httr::headers(req)

```
#### but HEAD does not work, also review httr:: calls here
```{r head}
req  <- httr::HEAD(
  "https://www.googleapis.com/oauth2/v1/userinfo",
  httr::config(token = auth.code) 
  )

httr::stop_for_status(req)
str(httr::content(req))


### identical to GET, but without the body
httr::HEAD("http://google.com")

### headers in response
httr::headers(httr::HEAD("http://google.com"))
```


## Examples
```{r one_video}

# prep for GET
if (!exists("api")) api <- get_api_codes()

l <- get_typical_values()
maxResults  <- l$maxResults
playlistId  <- l$playlistId
video_id = l$videoId
base_url <- "https://www.googleapis.com/youtube/v3/videos"


api_opts <- list(part = "snippet",
                 id = video_id,
                 maxResults = maxResults,
                 fields="items(snippet(title))",
                 key = api$api_key)


## TODO:  here r is https://   EXPLAIN
r  <- httr::HEAD(base_url, query = api_opts, httr::config(token= auth.code))


# WORKS!!!!
r  <- httr::GET(base_url, query = api_opts, httr::config(token= auth.code))
httr::stop_for_status(r)
httr::content(r)
str(httr::content(r))
```

TODO - not working, missing , in list()  -- is it TRUE, TRUE?
Given a channelId, returns total number of playlists
```{r playlist_count}
api <- get_api_codes()
api

base_url <- "https://www.googleapis.com/youtube/v3/playlists"

# mine =  ????
query  <- list(
						part="snippet, contentDetails",
    				channel_id="UClB5qWyXejlAwwkDAzJis-Q",
            mine = TRUE, 
						maxResults=3,
						fields="pageInfo(totalResults)",
						key = api$api_key
						)

r  <- httr::GET("https://www.googleapis.com/youtube/v3/playlists",
 							query= query,
 							config = httr::config(token = auth.code)
							) %>% httr::stop_for_status()

json_content  <- get_json(r)
count  <- json_content$pageInfo$totalResults
count
#jr_get_total_playlists(query) #142


# see HEAD?
httr::HEAD("https://www.googleapis.com/youtube/v3/playlists",
 							query= query,
 							config = config(token=auth.code))
```


Comments
```{r comments}

api  <- get_api_codes()
base_url <- "https://www.googleapis.com/youtube/v3/commentThreads"
l <- get_typical_values()

#playlistId  <- "PLbcglKxZP5PMZ7afIT7E2o9NwQIzqTI5l"

# fields , careful if split on mutliple lines, use paste
query  <- list(
	part="snippet,replies", 
	maxResults =l$maxResults, 
	fields=paste(sep=", ", "nextPageToken", 
			 "items(snippet(topLevelComment(snippet(videoId,textDisplay))))"
			 ),
	key = api$api_key, 
	pageToken = NULL, 
	videoId = l$videoId)

# google_token = base::getOption("google_token") 
# config  <- httr::config(google_token)

```

## 1st batch
```{r get}

r  <- httr::GET(base_url, query = query, httr::config(token= auth.code))
stop_for_status(r)
httr::content(r)
str(httr::content(r))


#comments  <- process_comments(r, comments)
comments  <- jr_get_batch_comments(base_url, query, config) 
comments
```

***

```{r knit_exit()} 
knitr::knit_exit()
```

\newpage

```{r render, eval=FALSE	} 
file <- ""
file  <- basename(file)
dir <- "rmd"

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```
