--- 
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"
output: 
  html_document:
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document:   
    latex_engine: lualatex  
    toc: true
    toc_depth:  4   
    keep_tex:  true  
    keep_md:   true  
  header-includes:  
    -  \usepackage{helvet}  
    -  \renewcommand{\familydefault}{\sfdefault}  
    -  \usepackage{ulem}
fontsize: 10pt   
geometry: margin=0.4in,top=0.25in   
TAGS:  httr2,
---


REF : GITHUB and GIST
https://httr2.r-lib.org/articles/httr2.html
```{r setup, include=FALSE		}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "      ##",
  error = TRUE,
  collapse = TRUE
)
library(httr2)
load_all()
```

#### show HEADERS

```{r setup_details}
##  replace httr2:: function with wrapper.  Makes default to NOT redact.

req_dry_run <- function(..., redact_headers = F) {
  httr2::req_dry_run(..., redact_headers = redact_headers)
}

##  SET/GET
Sys.setenv(FAKE = "joke")
Sys.getenv("FAKE")

system("echo hi")
system2("v=FAKE")
```


#### git should NOT pick this up
```{r}
writeLines(text = "FOO", con = "_secret_file")
readLines("_secret_file")
```

#### read API codes from ~/.Renviron and save to local file that git ignores
```{r}
## github token, for GIST only

HTTR2_GIST <- Sys.getenv("HTTR2_GIST")
HTTR2_GIST
writeLines(text = paste0("HTTR2_GIST=", HTTR2_GIST), con = " _HTTR2_GIST")
token <- HTTR2_GIST
```


###    GITHUB GISTS API

####    Authenication
```{r begin}
## use my person token (in ~/.Renviron)
token <- Sys.getenv("HTTR2_GIST")
token

req <- request("https://api.github.com/gists") %>%
  req_headers(Authorization = paste("token", token))

## note 'redacted', but httr2 knew to add header
## request OBJECT
req


req %>% req_dry_run()

## run it to see what sending to server
resp <- req %>% req_perform()
length(resp) # list 5, one is headers (26 list) and another is body (raw)
str(resp)

##  nested list, quite a bit
resp
resp |> resp_body_json()
```


####    At this point, have successfully access Gist api

Follow Hadley in checking errors and building out functions to work with github
gists.   Goal is;  upload gits

#### Deliberate error to see it:
```{r error}
resp <- request("https://api.github.com/gists") %>%
  req_url_query(since = "abcdef") %>%
  req_headers(Authorization = paste("token", token)) %>%
  req_perform()

#> Error: HTTP 422 Unprocessable Entity.
```
```{r error_fct}
gist_error_body <- function(resp) {
  body <- resp_body_json(resp)

  message <- body$message
  if (!is.null(body$documentation_url)) {
    message <- c(message, paste0("See docs at <", body$documentation_url, ">"))
  }
  message
}
gist_error_body(resp)
```

####   nicely printing errors
```{r}
request("https://api.github.com/gists") %>%
  req_url_query(since = "yesterday") %>%
  req_headers(Authorization = paste("token", token)) %>%
  req_error(body = gist_error_body) %>%
  req_perform()
```


#### rate limiting
```{r}
resp <- req %>% req_perform()
resp %>% resp_headers("ratelimit")
```

####   Finally, connect to the gist
```{r}
req_gist <- function(token) {
  request("https://api.github.com/gists") %>%
    req_headers(Authorization = paste("token", token)) %>%
    req_error(body = gist_error_body)
  # %>%
  # req_retry(
  #  is_transient = gist_is_transient,
  #  after = gist_after
  # )
}

# works
req_gist(token) %>% req_perform()
```

####    Upload
```{r}
req <- req_gist(token) %>%
  req_body_json(list(
    description = "This is my cool gist!",
    files = list(test.R = list(content = "print('Hi!')")),
    public = FALSE
  ))
req %>% req_dry_run()


# works !
resp <- req %>% req_perform()
resp

resp %>% resp_headers()
resp %>% resp_body_json()

# seems easier to read (if not manipulate)
resp %>% resp_raw()

id <- resp %>%
  resp_body_json() %>%
  .$id
id
```




