--- 
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"
output: 
  html_document:
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document:   
    latex_engine: lualatex  
    toc: true
    toc_depth:  4   
    keep_tex:  true  
    keep_md:   true  
  header-includes:  
    -  \usepackage{helvet}  
    -  \renewcommand{\familydefault}{\sfdefault}  
    -  \usepackage{ulem}
fontsize: 10pt   
geometry: margin=0.4in,top=0.25in   
TAGS:  httr2,
---

PURPOSE:    Use httr2 + github + oauth 2.0

REF : GITHUB and GIST
https://httr2.r-lib.org/articles/httr2.html

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)
library(httr2)
```

#### show HEADERS

```{r setup_details}

##  replace httr2:: function with wrapper.  Makes default to NOT redact.

req_dry_run  <- function(..., redact_headers=F) {
    httr2::req_dry_run(..., redact_headers=redact_headers)
}
```


####	Prefix file name with `_` (underscore) and git will not include it
(Example) 
```{r include=F, eval=F}
writeLines(text = "FOO", con = "_secret_file") 
readLines("_secret_file")

```

#### read API codes from ~/.Renviron and save to local file that git ignores
```{r  include=F, eval=F}
## github token, for GIST only

HTTR2_GIST  <- Sys.getenv("HTTR2_GIST")
HTTR2_GIST
writeLines(text = paste0("HTTR2_GIST=", HTTR2_GIST), con= " _HTTR2_GIST")
token  <- HTTR2_GIST
```


###   Follow Vignette for OAUTH and GITHUB 

####    Authenication
```{r begin}

##	Github does not permit standalone oauth clients.
##  This is Hadley's client/  I can't recreate my own:  what is URL??


client <- oauth_client(
  id = "28acfec0674bb3da9f38",
  secret = obfuscated("J9iiGmyelHltyxqrHXW41ZZPZamyUNxSX1_uKnvPeinhhxET_7FfUs2X0LLKotXY2bpgOMoHRCo"),
  token_url = "https://github.com/login/oauth/access_token",
  name = "hadley-oauth-test"
)


client

##	Per Hadley, use flow:  auth_code

##  github window pops up to authorizee 
##	auth_url is endpoint to obtain user
token <- oauth_flow_auth_code(client, auth_url = "https://github.com/login/oauth/authorize")

#	token is list, token_type, access_token itself, scope
# in this case, has no scope!
token
str(token)
```


####    At this point, we have access token and we can make request (user info)
			To do so, we tell github we send the same token as a `bearer_token`
```{r}

# First, he says do htis and it prints "jim"

request("https://api.github.com/user") %>% 
  req_auth_bearer_token(token$access_token) %>% 
  req_perform() %>% 
  resp_body_json() %>%
  .$name
# 
```


####	Easier way:  let httr2 handled intermediate details (ie token) 
```{r}

# Then he says this is better, which prints stuff about me.
##	Again browser pops up, but authentication is done automatically.
request("https://api.github.com/user") %>% 
  req_oauth_auth_code(client, auth_url = "https://github.com/login/oauth/authorize") %>% 
  req_perform() 


##	adding this piece prints to conosole as list
# %>% 
# resp_body_json()


  ## find cached tokens?
rappdirs::user_cache_dir("httr2")
# [1] "/home/jim/.config/cache/httr2"

dir(rappdirs::user_cache_dir("httr2"), recursive = TRUE)
# character(0)
```




