--- 
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"
output: 
  html_document:
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document:   
    latex_engine: lualatex  
    toc: true
    toc_depth:  4   
    keep_tex:  true  
    keep_md:   true  
  header-includes:  
    -  \usepackage{helvet}  
    -  \renewcommand{\familydefault}{\sfdefault}  
    -  \usepackage{ulem}
fontsize: 10pt   
geometry: margin=0.4in,top=0.25in   
TAGS:  httr2,
---
PURPOSE:    HTTR2::   practice with OAUTH2 google People API
Reproduce what browser can do.


REF : 
Google:   project;  jrGooglePeopleapi
REF:    https://www.daimto.com/how-to-get-a-google-access-token-with-curl/

https://httr2.r-lib.org/articles/httr2.html
```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)
library(httr2)
```



####    Step 1, get AUTH.CODE (via Browser)
```
Put into browser to (1) authorize (2) return AUTH CODE
Goal:  Do it R.
```

```
## from httr:   useful?
  httr::oauth_endpoints("google")
# <oauth_endpoint>
#  authorize: https://accounts.google.com/o/oauth2/auth
#  access:    https://accounts.google.com/o/oauth2/token
#  validate:  https://www.googleapis.com/oauth2/v1/tokeninfo
#  revoke:    https://accounts.google.com/o/oauth2/revoke
```

####    For Google People API
```{r usefu}

#   from ~/.Renviron
    client_id  <- Sys.getenv("PEOPLE_CLIENT_ID")
    client_secret  <- Sys.getenv("PEOPLE_CLIENT_SECRET")

endpoint = "https://accounts.google.com/o/oauth2/v2/auth"
scope="https://www.googleapis.com/auth/userinfo.profile"
```

####    Get auth.code (via broswer)
```{r auth}
##  paste b into browser
    b  <- paste0("https://accounts.google.com/o/oauth2/v2/auth?client_id=",
        client_id,  "&",
        "redirect_uri=urn:ietf:wg:oauth:2.0:oob&scope=https://www.googleapis.com/auth/userinfo.profile&response_type=code")

##  Retrieve auth.code from browser and paste here
auth.code  <- "4/1AX4XfWisGY43zYSJG_Cd3RiZOS0sg9jg3VjaEmSocGfeUaDrcflvlwBauYU"

```


#### Exchange auth.code 
```
curl -s \
--request POST \
--data "code=4/1AY0e-g7BhBt0QU9f5HTgNDGNR1GYtH12q4xvgL_D2Q34A&client_id=XXXX.apps.googleusercontent.com&client_secret=zYAoXDam3mqsdwabh3dQ3NTh&redirect_uri=urn:ietf:wg:oauth:2.0:oob&grant_type=authorization_code" \

https://accounts.google.com/o/oauth2/token 
```

```{r exchange}
##  For me:
data  <- paste0("code=",auth.code,"&", 
                "client_id=", client_id, "&",
                "client_secret=",client_secret,"&",
                "redirect_uri=urn:ietf:wg:oauth:2.0:oob&grant_type=authorization_code")
data
 "code=4/1AX4XfWisGY43zYSJG_Cd3RiZOS0sg9jg3VjaEmSocGfeUaDrcflvlwBauYU&client_id=358088442289-amr4b5f5l1h9jicffu12d9t1vooiv10d.apps.googleusercontent.com&client_secret=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&redirect_uri=urn:ietf:wg:oauth:2.0:oob&grant_type=authorization_code"

## in httr2

token_url  <- "https://accounts.google.com/o/oauth2/token" 

request(token_url) |> req_method("POST") |> req_body_raw(data) |> req_dry_run()


# error 400, "invalid \ncode=4/1....43\n^" thinks JSON
request(token_url) |> req_method("POST") |> req_body_raw(data) |> req_perform() 


req_url_query(data) |> req_dry_run() request(token_url) |> req_url_path_append(data) |> req_dry_run()
request(token_url) |> req_url_path_append(data) |> req_perform()

request(token_url) |> req_body_raw(data) |> req_dry_run()
request(token_url) |> req_verbose() |> req_body_raw(data) |> req_perform() |> with_verbosity()
last_response()
```


```
####    Create client to youtube
```{r client}

myapp = httr2::oauth_client(
        id =    client_id,
        token_url = endpoint, 
        name = "first_people_api"            
    )

myapp


## get AUTH CODE:  seem to be 2 ways
resp = req_oauth_auth_code(req = httr2::request("https://accounts.google.com/o/oauth2/v2/auth"), 
                    client= myapp,
                    auth_url = "https://accounts.google.com/o/oauth2/v2/auth")

resp
```
```{r}
req  <- request("https://accounts.google.com/o/oauth2/v2/auth?client_id=358088442289-amr4b5f5l1h9jicffu12d9t1vooiv10d.apps.googleusercontent.com&redirect_uri=urn:ietf:wg:oauth:2.0:oob&scope=https://www.googleapis.com/auth/userinfo.profile&response_type=code")

req
## get no browser???
res  <- req_perform(req)
```

```{r token}
token  <-   oauth_flow_auth_code(client = myapp, 
                     auth_url = "https://accounts.google.com/o/oauth2/auth",
                     scope = scope
                     )
token
```


##  LEGACY
#### GET can have header, query, not body
#### get a req object, using httpbin, GET http://httpbin.org
```{r}
##  return what is sent
req <- request("https://httpbin.org/get")
req

## tack on query
req2 <- request("https://httpbin.org/get?q=joe")
req2

## now build, httr2 adds default headers
req %>% req_dry_run()


##  quote works
req |> req_headers(name =  "jim", location =  quote(eugene) )
```

##  SCOPE 3 (BEST)
  - USE THIS auth.code for most work
  - Add scope for various youtube access.
  - youtube.force-ssl needed to retrieve user's playists, videos in each
```{r youtube_scopes}
#  
{
scope = 
  c("https://www.googleapis.com/auth/userinfo.profile",
  "https://www.googleapis.com/auth/userinfo.email",
  "https://www.googleapis.com/auth/youtube",  # manage
  "https://www.googleapis.com/auth/youtube.readonly",
  "https://www.googleapis.com/auth/youtube.force-ssl"
   )
}
 ```  
## Get auth.code | token ....

```{r render, eval=FALSE	} 
file <- ""
file  <- basename(file)
dir <- "rmd"

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```
