
	 vim:linebreak:nowrap:nospell:cul tw=78 fo=tqlnr foldcolumn=3 
	 
--- 
# Spaces, no Tabs
title: Template for .Rmd 
output: 
  pdf_document: 
    latex_engine: xelatex
toc: TRUE 
toc_depth:  1 
fontsize: 12pt 
geometry: margin=0.5in,top=0.25in 

---
/home/jim/.config/nvim/templates/skeleton.Rmd
othercomments
---
<!-- 
set cul   "cursorline
cc=+1			"colorcolumn is 1 more than tw
-->

<!--  commments -->

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  
											comment="      ##",  
											error=TRUE, 
											collapse=TRUE) 
```

<!--  RENDER:  see bottom -->

```{r library, include=FALSE		}
library(jimTools) 
``` 

HERE -- What is playlistId for "Watch Later"  ?
```{r begin}
l <- get_typical_yt()
maxResults  <- l$maxResults
playlistId  <- l$playlistId
video_id = l$videoId
base_url  <- "https://www.googleapis.com/youtube/v3/playlists"
```


```{r}

api_opts <- list(part = "snippet",
                 id = video_id,
                 maxResults = maxResults,
                 fields="items(snippet(title))",
                 key = api$api_key)

#DELETE https://www.googleapis.com/youtube/v3/playlists
r <- httr::GET(base_url, query = api_opts) 
httr::content(r)

***

```{r knit_exit()} 
knitr::knit_exit() 
```

/newpage

```{r render, eval=FALSE	} 
file <- "" 
file  <- basename(file) 
dir <-"rmd"

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```
